---
title: "Biden Polling"
format: html
author: Luke Li
execute: 
  echo: false
  message: false
---


```{r}
#| message: false
library(tidyverse)
library(marginaleffects)
library(tidymodels)
library(broom)
library(ggplot2)
library(dplyr)
library(scales)
poll_data <- tibble(biden = as.factor(c(rep("Yes", 655), 
                                        rep("No", 904)))) |> 
                slice_sample(prop = 1)
```

```{r}
#| message: false
#| cache: true
#| include: false
fit_biden <- logistic_reg() |> 
  fit(biden ~ 1, data = poll_data)
tidy(fit_biden, conf.int = TRUE)
```

## Table and Plot
```{r}
library(gt)
library(dplyr)

# Original tidy output
results <- tibble::tibble(
  term = "(Intercept)",
  estimate = -0.322,
  std.error = 0.0513,
  conf.low = -0.423,
  conf.high = -0.222
)

# Format the table
results %>%
  select(term, estimate, std.error, conf.low, conf.high) %>%
  rename(
    Term = term,
    Estimate = estimate,
    `Std. Error` = std.error,
    `95% CI Lower` = conf.low,
    `95% CI Upper` = conf.high
  ) %>%
  gt() %>%
  fmt_number(
    columns = c(Estimate, `Std. Error`, `95% CI Lower`, `95% CI Upper`),
    decimals = 3
  ) %>%
  tab_header(
    title = "Logistic Regression Coefficients",
    subtitle = "Estimated log-odds for predicting support for Biden"
  )
```

```{r}
# Recreate the plot based on avg_predictions() output
avg_predictions(fit_biden, type = "prob") %>%
  filter(group == "Yes") %>%
  ggplot(aes(x = "", y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  size = 1.2,
                  color = "darkblue") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0.38, 0.46),
                     breaks = seq(0.38, 0.46, 0.02)) +
  labs(title = "Support for President Biden in March 2024",
       subtitle = "42% is not a good sign for an incumbent seeking reelection",
       caption = "Source: YouGov poll, March 2024.",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 12, color = "gray40"),
        plot.caption = element_text(size = 10, color = "gray60", hjust = 1),
        axis.text.y = element_text(size = 11),
        panel.grid.major.y = element_line(color = "gray90"),
        panel.grid.minor.y = element_line(color = "gray95"))
```

## Description
Voting for the president of the United States often feels unpredictable, but there are many variables that influence each voter's choice that can foresee the outcome. Using March 2024 YouGov survey data from 1,559 U.S. adults, we estimate the proportion of votes Joe Biden will receive in the November election. A potential weakness of our model is that it uses a relatively small sample dataset size of only 1,599 U.S. adults whereas the total voting population is in the hundreds of millions, thus resulting in issues with representativeness. We model voter preference in the 2024 U.S. presidential election with the probability that a respondent supports Biden.  We use a logistic function with no predictors, capturing the overall proportion of support in the population. The outcome variable is binary, with ‘Yes’ for Biden supporters and ‘No’ for non-supporters. A quantity of interest of our project was the proportion of voters that would vote for Biden in the 2024 US presidential election, and based off of our data we found a 95% confidence interval between −0.423 and −0.222 for log-odds (39% to 45% in normal probability). The estimates for quantities of interest might be wrong because the data we obtained came from months before the election, and last-minute voters might have different choices for who they want to elect. As a result, the real proportion of Biden voters could be higher or lower than our predicted 42%.


## Mathematical Models
$$
\log\left( \frac{\Pr(Y = 1)}{1 - \Pr(Y = 1)} \right) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + \beta_4 X_4 + \cdots
$$

$$
\log\left( \frac{\Pr(\text{biden} = \text{Yes})}{1 - \Pr(\text{biden} = \text{Yes})} \right) = -0.322
$$

